Home

### 2022-03-09 analysis/Orthofinder.Rmd
add better groups

seagrass_venn <- ggplot() +
    geom_sf(aes_string(fill="count"), data = data@region) +
    geom_sf(aes_string(color = "id"), data = data@setEdge, show.legend = F,
            lty = 'solid', size = 1, color='gray') +
    geom_sf_text(aes_string(label = "name"), data = data@setLabel,
                 size = NA, fontface='italic',
                 color = 'black') +
    theme_void() +
     geom_sf_label(aes_string(label='both'),
                             data = region_label,
                             alpha= 0,
                             color = 'black',
                             size = NA,
                             lineheight = 0.85,
                             label.size = NA) +
  scale_fill_gradientn(colours=wes_palette("Zissou1", 100, type = "continuous")) + 
  theme(legend.position = "none") + 
  scale_x_continuous(expand = expansion(mult = .2)) #trick from https://github.com/gaospecial/ggVennDiagram/blob/9435aa0ab4abb470c670ecb938c71576461ccedc/vignettes/using-ggVennDiagram.Rmd#L65
seagrass_venn
```

@@

groups_in_all_seagrasses <- union(union(union(big_list[['Z. muelleri']], big_list[['A. antarctica']]), big_list[['P. australis']]), big_list[['Z. marina']])

groups_lost_in_A_antarctica <- setdiff(groups_in_all_seagrasses, big_list[['A. antarctica']])
genes_lost_in_A_antarctica <- gene_per_spec %>% 
  filter(name != 'A. antarctica', Orthogroup %in% groups_lost_in_A_antarctica) %>% 
  separate_rows(value, sep=',') %>% pull(value) %>% str_trim()

groups_lost_in_P_australis <- setdiff(groups_in_all_seagrasses, big_list[['P. australis']])
genes_lost_in_P_australis <- gene_per_spec %>% 
  filter(name != 'P. australis', Orthogroup %in% groups_lost_in_P_australis) %>% 
  separate_rows(value, sep=',') %>% pull(value) %>% str_trim()

groups_lost_in_Z_marina <- setdiff(groups_in_all_seagrasses, big_list[['Z. marina']])
genes_lost_in_Z_marina <- gene_per_spec %>% 
  filter(name != 'Z. marina', Orthogroup %in% groups_lost_in_Z_marina) %>% 
  separate_rows(value, sep=',') %>% pull(value) %>% str_trim()

groups_lost_in_Z_muelleri <- setdiff(groups_in_all_seagrasses, big_list[['Z. muelleri']])
genes_lost_in_Z_muelleri <- gene_per_spec %>% 
  filter(name != 'Z. muelleri', Orthogroup %in% groups_lost_in_Z_muelleri) %>% 
  separate_rows(value, sep=',') %>% pull(value) %>% str_trim()
```

@@

>>>>

seagrass_venn <- ggplot() +
    geom_sf(aes_string(fill="count"), data = data@region) +
    geom_sf(aes_string(color = "id"), data = data@setEdge, show.legend = F,
            lty = 'solid', size = 1, color='gray') +
    geom_sf_text(aes_string(label = "name"), data = data@setLabel,
                 size = NA, fontface='italic',
                 color = 'black') +
    theme_void() +
     geom_sf_label(aes_string(label='both'),
                             data = region_label,
                             alpha= 0,
                             color = 'black',
                             size = NA,
                             lineheight = 0.85,
                             label.size = NA) +
  scale_fill_gradientn(colours=wes_palette("Zissou1", 3, type = "continuous")) + 
  theme(legend.position = "none") + 
  scale_x_continuous(expand = expansion(mult = .2)) #trick from https://github.com/gaospecial/ggVennDiagram/blob/9435aa0ab4abb470c670ecb938c71576461ccedc/vignettes/using-ggVennDiagram.Rmd#L65
seagrass_venn
```

@@

groups_in_all_seagrasses_union <- union(union(union(big_list[['Z. muelleri']], big_list[['A. antarctica']]), big_list[['P. australis']]), big_list[['Z. marina']])
genes_in_all_seagrasses_union <- gene_per_spec %>% 
  filter(name %in% c('A. antarctica', 'P. australis', 'Z. muelleri', 'Z. marina'), Orthogroup %in% groups_in_all_seagrasses_union) %>% 
  separate_rows(value, sep=',') %>% pull(value) %>% str_trim()

groups_in_all_seagrasses_intersect <- intersect(intersect(intersect(big_list[['Z. muelleri']], big_list[['A. antarctica']]), big_list[['P. australis']]), big_list[['Z. marina']])
genes_in_all_seagrasses_intersect <- gene_per_spec %>% 
  filter(name %in% c('A. antarctica', 'P. australis', 'Z. muelleri', 'Z. marina'), Orthogroup %in% groups_in_all_seagrasses_intersect) %>% 
  separate_rows(value, sep=',') %>% pull(value) %>% str_trim()

groups_lost_in_A_antarctica <- setdiff(groups_in_all_seagrasses_union, big_list[['A. antarctica']])
genes_lost_in_A_antarctica <- gene_per_spec %>% 
  filter(name != 'A. antarctica', Orthogroup %in% groups_lost_in_A_antarctica) %>% 
  separate_rows(value, sep=',') %>% pull(value) %>% str_trim()

groups_lost_in_P_australis <- setdiff(groups_in_all_seagrasses_union, big_list[['P. australis']])
genes_lost_in_P_australis <- gene_per_spec %>% 
  filter(name != 'P. australis', Orthogroup %in% groups_lost_in_P_australis) %>% 
  separate_rows(value, sep=',') %>% pull(value) %>% str_trim()

groups_lost_in_Z_marina <- setdiff(groups_in_all_seagrasses_union, big_list[['Z. marina']])
genes_lost_in_Z_marina <- gene_per_spec %>% 
  filter(name != 'Z. marina', Orthogroup %in% groups_lost_in_Z_marina) %>% 
  separate_rows(value, sep=',') %>% pull(value) %>% str_trim()

groups_lost_in_Z_muelleri <- setdiff(groups_in_all_seagrasses_union, big_list[['Z. muelleri']])
genes_lost_in_Z_muelleri <- gene_per_spec %>% 
  filter(name != 'Z. muelleri', Orthogroup %in% groups_lost_in_Z_muelleri) %>% 
  separate_rows(value, sep=',') %>% pull(value) %>% str_trim()

@@

fileConn <- file('data/Lost_present_gene_lists/Genes_in_all_seagrasses_union.txt')
writeLines(genes_in_all_seagrasses_union, fileConn)
close(fileConn)

fileConn <- file('data/Lost_present_gene_lists/Genes_in_all_seagrasses_intersect.txt')
writeLines(genes_in_all_seagrasses_intersect, fileConn)
close(fileConn)

### 2022-03-09 analysis/index.Rmd
Add missing files
wflow_publish(files = list.files("analysis/", pattern = "*Rmd",     full.names = T))
wflow_publish(files = c("analysis/*"))
wflow_publish("analysis/index.Rmd")
add better groups

This website collects comparisons of Amphibolis and Posidonia comparative analyses.

[Repeat comparison plots](plot.html)

[Phylogenies](OTT.html)

>>>>

This website collects comparisons of *Amphibolis* and *Posidonia* comparative analyses.

[Repeat comparison plots](plot.html) - Comparing genome sizes and repeat/TE content

[Phylogenies](OTT.html) - plotting just phylogenies

[Clustering results](Orthofinder.html) - analysing Orthofinder clustering results

[R gene plotting](plotRgenes.html) - making phylogenies and showing R-gene number differences

[Gene Loss comparison by reads](GeneLossComparisonReads.html) - making heatmaps and barcharts to compare read alignments

[GO enrichment](GOenrichment.html) - running topGO and REVIGO to make nice plots of GO-enrichment

[GO and Ortho](GO_and_ortho.html) - merging plots from GO enrichment and Orthofinder analysis
